Generalized Disappointment Aversion and heavy-tail property of equity return distributions

### 2017-04-02 cv/20sec/template.tex
Revised my CV.

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

@@

\aboutme{Alice is a sensible prepubescent girl from a wealthy English family who finds herself in a strange world ruled by imagination and fantasy. Alice feels comfortable with her identity and has a strong sense that her environment is comprised of clear, logical, and consistent rules and features. Alice's familiarity with the world has led one critic to describe her as a "disembodied intellect". Alice displays great curiosity and attempts to fit her diverse experiences into a clear understanding of the world.} % To have no About Me section, just remove all the text and leave \aboutme{}

@@

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{{pursuer of rabbits/5.8},{good manners/4},{outgoing/4.3},{polite/4},{Java/0.01}}

@@

% Skill text section, each skill must have a value between 0 an 6
\skillstext{{lovely/4},{narcissistic/3}}

@@

\section{Interests}

The heroine and the dreamer of Wonderland; Alice is the principal character.

@@

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{since 1865}{Ph.D. {\normalfont candidate in Computer Science}}{Wonderland}{\emph{A Quantified Theory of Social Cohesion.}}
	\twentyitem{1863-1865}{M.Sc. magna cum laude}{Wonderland}{Majoring in Computer Science}
	\twentyitem{1861-1863}{B.Sc. magna cum laude}{Wonderland}{Majoring in Computer Science}
	\twentyitem{1856-1861}{High school}{Wonderland}{Specializing in mathematics and physics.}
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 PUBLICATIONS
%----------------------------------------------------------------------------------------

@@

\begin{twentyshort} % Environment for a short list with no descriptions
	\twentyitemshort{1865}{Chapter One, Down the Rabbit Hole.}
	\twentyitemshort{1865}{Chapter Two, The Pool of Tears.}
	\twentyitemshort{1865}{Chapter Three,  The Caucus Race and a Long Tale.}
	\twentyitemshort{1865}{Chapter Four,  The Rabbit Sends a Little Bill.}
	\twentyitemshort{1865}{Chapter Five,  Advice from a Caterpillar.}
	%\twentyitemshort{<dates>}{<title/description>}
\end{twentyshort}

%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

\section{Awards}

\begin{twentyshort} % Environment for a short list with no descriptions
	\twentyitemshort{1987}{All-Time Best Fantasy Novel.}
	\twentyitemshort{1998}{All-Time Best Fantasy Novel before 1990.}
	%\twentyitemshort{<dates>}{<title/description>}
\end{twentyshort}

@@

\section{Experience}

@@

%\newpage % Start a new page

%\makeprofile % Print the sidebar

>>>>

%% \documentclass[letterpaper]{twentysecondcv} % a4paper for A4
\documentclass[a4paper]{twentysecondcv} % a4paper for A4

@@

\aboutme{
  \begin{itemize}
  \item Ph.D of Mathematical Statistics at Copenhagen University
  \item M.Sc. of Mathematical Physics
  \item M.Sc. of Computer Science
  \item 7 years work experience in programming 
  \item strong in statistical analysis \& numerical methods
  \end{itemize}
} % To have no About Me section, just remove all the text and leave \aboutme{}

@@

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills {{Python/3},{SQL/4},{GNU Scientific Library/5},{Matlab/5.2},{R/5.8},{C/5},{C++/5}}

@@

% Skill text section, each skill must have a value between 0 an 6
%% \skillstext{{lovely/4},{narcissistic/3}}

@@

%% \section{Summary}

@@

\begin{minipage}{0.15\linewidth}
  Oct. 2014 - Sep. 2017
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item Ph.D. in Mathematical Statistics
  \item Copenhagen University
  \item Areas of research:
    \begin{itemize}
      \item {\bf Time series analysis}: ARIMA, GARCH, stochastic volatility
        models
      \item {\bf Asset allocation \& risk management}: Principle component
        analysis; optimization of investor utility functions; extreme
        value theory
      \item {\bf Numerical methods}: Importance sampling, numerical
        optimization, estimation of GARCH(p,q) tail indices
    \end{itemize}
  \end{itemize}
\end{minipage}

\vspace{3mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2011 - June 2014
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item M.Sc. in Mathematical Physics
  \item Lund University
  \item Thesis project: Distribution of eigenvalues of large
    sample covariance matrices in the infinite dimensional limit with
    a focus on the influence of autocorrelations and heavy tails. The
    theoretical derivation is based on the {\it free probability
      theory} and is checked against {\it intraday tick-by-tick
      prices} of high-volume Swedish stocks.
  \item Course work:    
    \begin{itemize}
      \item Mathematical methods of Physics and Engineering
      \item Statistical mechanics, Quantum mechanics, General
        relativity
    \end{itemize}
  \end{itemize}
\end{minipage}

%% \begin{minipage}[b]{0.2\linewidth}
%%   Oct. 2014 - Sep. 2017
%% \end{minipage} \hfill
%% \begin{minipage}{0.8\linewidth}
%%   \begin{itemize}
%%   \item Ph.D. in Mathematical Statistics
%%   \item Copenhagen University
%%   \item \emph{portfolio \& risk management} Balbla. Oh my god, I have
%%     to write a lot more about my research
%%   \end{itemize}
%% \end{minipage}

@@

\begin{itemize}
\item Davis, R.A., Heiny, J., Mikosch, T. and {\bf Xie, X.},
  2016. {\it Extreme value analysis for the sample autocovariance
    matrices of heavy-tailed multivariate time series}.
  \underline{Extremes}, 19(3), pp.517-547.

  {\small
  We provide, among others, a limit theory for the largest eigenvalues
  of a sample covariance matrix of heavy-tailed, possibly linearly
  dependent data with infinite dimensions. We prove weak convergence of
  the point process of the largest eigenvalues to Poisson or cluster
  Poisson processes and, based on this convergence result, derive limit
  laws of functions of the ordered eigenvalues.}

\item Jan\ss en, A., Mikosch, T., Rezapour, M., {\bf Xie, X},
  2016. {\it The eigenvalues of the sample covariance matrix of a
    multivariate heavy-tailed stochastic volatility model}.
  To appear in the \underline{Bernoulli Journal}.

  {\small
  We derive multivariate $\alpha$-stable limit distributions of the
  sample covariance matrix when the sample size was large. We
  consider two possibilities of heavy-tails: 1. the innovation
  sequence is heavy tailed; and 2. the volatility sequence is
  heavy-tailed. While the eigen system of the first case is shown to
  resemble that of i.i.d data, the eigen system in the second case is
  found to allow dependencies in their limiting distributions, which
  are determined by the structure of the volatility sequence.}
\end{itemize}

\section{Papers in Finalization}
\begin{itemize}
\item Mikosch, T., de Vries, C., {\bf Xie, X.}, 2017,
  {\it Generalized Disappointment Aversion and heavy-tail property of
    equity return distributions}

  {\small
    We study the heavy tail properties of real-world equity return
    distributions and, based on the framework of Generalized
    Disappointment Aversion, derive how an investor's preference varies
    with the tail distribution characteristics, namely the tail index and
    the scale parameter. We find, when the equity return is t-distributed,
    the GDA preference actually decreases with the degree of freedom of
    the distribution, i.e. the tail index; we interprete this as a
    consequence of the symmetry of the distribution. When the equity
    return is assumed to have a shifted Pareto distribution with
    independent parameters of the left and the right tails, we find the
    GDA preference increasing with both the lower tail index and the scale
    parameter. We attribute this to the risk avert nature of rational
    investors. By numerical methods, optimal asset allocation is also
    solved in both cases.
  }
\end{itemize}
%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

%% \section{Awards}

%% \begin{twentyshort} % Environment for a short list with no descriptions
%% 	\twentyitemshort{1987}{All-Time Best Fantasy Novel.}
%% 	\twentyitemshort{1998}{All-Time Best Fantasy Novel before 1990.}
%% 	%\twentyitemshort{<dates>}{<title/description>}
%% \end{twentyshort}

@@

\newpage % Start a new page

\section{Work Experience}

@@

### 2017-04-02 papers/FX/draft.tex
Revised my CV.

\title{Tail Indices and Scale Parameters in Financial Time Series}
\author{Thomas Mikosch, Casper de Vries, Xie Xiaolei}
\date{\today}
\begin{document}
\maketitle

\begin{abstract}
We consider an investor with preferences that accord with Generalized
Disappointment Aversion. Such an investor cares about downside risk and
we assume he recognizes the heavy tail feature of asset return
distributions. We argue that when a market is dominated by rational
investors of this kind, the return distributions of equities that are
actively traded in this market must have very similar tail indices. We
also show, in contrast, the scale parameters of the return
distributions may differ hugely from one another.

@@

In this work empirical results are also presented and they appear
to support the conclusion that the tail indices are very similar,
with respect to the confidence bands of estimation.
\end{abstract}

\section{Introduction}
It is generally believed that the utility function of an
investor is increasing and concave -- as John H. Cochrane
put it, ``the last bite is never as satisfying as the first''
\cite{cochrane2009asset}. This implies investors are repelled to a
larger extent by large losses than they are tempted by large gains. 
Furthermore, it is a stylized fact that equity return distributions
are heavy-tailed (see e.g. Jansen and de Vries \cite{jansen1991frequency}).
In particular, the lower-tail of an equity distribution is often heavier
than the upper-tail of the same distribution.

>>>>

\title{Generalized Disappointment Aversion and heavy-tail property of
  equity return distributions}
\author{Thomas Mikosch, Casper de Vries, Xie Xiaolei}
\date{\today}
\begin{document}
\maketitle

\begin{abstract}
We study the heavy tail properties of real-world equity return
distributions and, based on the framework of Generalized
Disappointment Aversion, derive how an investor's preference varies
with the tail distribution characteristics, namely the tail index and
the scale parameter. We find, when the equity return is t-distributed,
the GDA preference actually decreases with the degree of freedom of
the distribution, i.e. the tail index; we interprete this as a
consequence of the symmetry of the distribution. When the equity
return is assumed to have a shifted Pareto distribution with
independent parameters of the left and the right tails, we find the
GDA preference increasing with both the lower tail index and the scale
parameter. We attribute this to the risk avert nature of rational
investors. By numerical methods, optimal asset allocation is also
solved in both cases.

%% We consider investors with preferences that accord with Generalized
%% Disappointment Aversion. Such an investor cares about downside risk and
%% we assume he recognizes the heavy tail feature of asset return
%% distributions. We argue that when a market is dominated by rational
%% investors of this kind, the return distributions of equities that are
%% actively traded in this market must have very similar tail indices. We
%% also show, in contrast, the scale parameters of the return
%% distributions may differ hugely from one another.

%% It is generally believed that the utility function of an
%% investor is increasing and concave -- as John H. Cochrane
%% put it, ``the last bite is never as satisfying as the first''
%% \cite{cochrane2009asset}. This implies investors are more repelled
%% by large losses than they are tempted by large gains. 
%% Furthermore, it is a stylized fact that equity return distributions
%% are heavy-tailed (see e.g. Jansen and de Vries
%% \cite{jansen1991frequency}).
%% In particular, the lower-tail of an equity distribution is often heavier
%% than the upper-tail of the same distribution.

%% We explore in this paper the market implications of investor
%% preferences and the heavy-tail property of equity return
%% distributions.

@@

%% In this work empirical results are also presented and they appear
%% to support the conclusion that the tail indices are very similar,
%% with respect to the confidence bands of estimation.
\end{abstract}

\section{Introduction}
It is generally believed that the utility function of an
investor is increasing and concave -- as John H. Cochrane
put it, ``the last bite is never as satisfying as the first''
\cite{cochrane2009asset}. This implies investors are more repelled
by large losses than they are tempted by large gains. 
Furthermore, it is a stylized fact that equity return distributions
are heavy-tailed (see e.g. Jansen and de Vries \cite{jansen1991frequency}).
In particular, the lower-tail of an equity distribution is often heavier
than the upper-tail of the same distribution.
